---
title: "Goodreads"
output:
  html_document:
    fig-width: 8
    fig-height: 4
    code-fold: true
    toc: true
    theme: united
---

## Goodreads Data

# Loading Packages

```{r}

library(tidyverse)
library(corrplot)
library(pheatmap)


```

# Loading Data

```{r}

books <- read_csv("../input/goodreadsbooks/books.csv")

```

# Data Summary

```{r}

books %>% summary
```

# Ratings Distribution

```{r}

books %>%
  ggplot() +
  aes(x = (average_rating)) +
  geom_histogram(bins = 50) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )


```

# Number of Pages Distribution

```{r}


books %>%
  ggplot() +
  aes(x = (num_pages)) +
  geom_histogram(bins = 50) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )

```

# Most Occurring Books in the data

```{r}


books %>%
  group_by(title) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(25) %>%
  ggplot(aes(
    x = reorder(title, count),
    y = count,
    fill =as.factor(count)
  )) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(breaks = c(1:10)) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank())



```

# Most Common Languages

```{r}

books %>%
  group_by(language_code) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(10) %>%
  ggplot(aes(
    x = reorder(language_code, -count),
    y = count,
    fill =as.factor(count)
  )) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank())
```

# Most Rated Books

```{r}

books %>% 
  arrange(desc(ratings_count)) %>% 
  head(15) %>% 
    ggplot(aes(
    x = reorder(title, ratings_count),
    y = ratings_count,
    fill =as.factor(ratings_count)
  )) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank()) +
  coord_flip()
  
```

# Authors with most number of books

```{r}


books %>% 
  group_by(authors) %>% 
  summarise(total_books = n()) %>% 
  arrange(desc(total_books)) %>% 
  head(15) %>% 
  ggplot(aes(
    x = reorder(authors, total_books),
    y = total_books,
    fill =as.factor(total_books)
  )) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank()) +
  coord_flip()
  
```

# Books with the most reviews

```{r}


books %>% 
  arrange(desc(text_reviews_count)) %>% 
  head(15) %>% 
    ggplot(aes(
    x = reorder(title, text_reviews_count),
    y = text_reviews_count,
    fill =as.factor(text_reviews_count)
  )) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank()) +
  coord_flip()
  
```

# Longest Books (By Page Count)

```{r}


books %>% 
  arrange(desc(num_pages)) %>% 
  head(7) %>% 
    ggplot(aes(
    x = reorder(title, num_pages),
    y = num_pages,
    fill =as.factor(num_pages)
  )) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank()) +
  coord_flip()
  

```

# Most common publishers

```{r}


books %>% 
  group_by(publisher) %>% 
  summarise(total_books = n()) %>% 
  arrange(desc(total_books)) %>% 
  head(15) %>% 
  ggplot(aes(
    x = reorder(publisher, total_books),
    y = total_books,
    fill =as.factor(total_books)
  )) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank()) +
  coord_flip()
```

# Highest Rated Books

```{r}


books %>% 
  arrange(desc(average_rating)) %>% 
  head(15)

books %>% 
  arrange(desc(average_rating)) %>% 
  head(15) %>% 
    ggplot(aes(
    x = reorder(title, average_rating),
    y = average_rating,
    fill =as.factor(title)
  )) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text = element_text(size = 4)) +
  coord_flip()
```

# Lowest Rated Books

```{r}


books %>%
  filter(average_rating !=0) %>% 
  arrange(desc(average_rating)) %>% 
  head(15)

books %>%
  filter(average_rating !=0) %>% 
  arrange(desc(average_rating)) %>% 
  head(15) %>% 
    ggplot(aes(
    x = reorder(title, 
                average_rating),
    y = average_rating,
    fill =(average_rating)
  )) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank()) +
  coord_flip()
```

# Ratings vs Reviews Count Correlation

```{r}



books %>%
  ggplot(aes(x = ratings_count,
             y = text_reviews_count)) +
  geom_point() +
  geom_smooth(formula = y ~ x,
              method = lm) +
  theme_minimal()
```

# Average Ratings vs Reviews Correlation?

```{r}


books %>%
  ggplot(aes(y = average_rating,
             x = text_reviews_count)) +
  geom_point() +
  geom_smooth(formula = y ~ x,
              method = lm) +
  theme_minimal()

```

# Average Ratings vs Ratings Correlation?

```{r}


books %>%
  ggplot(aes(y = average_rating,
             x = ratings_count)) +
  geom_point() +
  geom_smooth(formula = y ~ x,
              method = lm) +
  theme_minimal()

```

# Average Ratings vs Num Pages Correlation?

```{r}



books %>%
  ggplot(aes(y = average_rating,
             x = num_pages)) +
  geom_point() +
  geom_smooth(formula = y ~ x,
              method = lm) +
  theme_minimal()

```

# Correlation between numeric data

```{r}


books %>%
  select(ratings_count,
         text_reviews_count,
         num_pages,
         average_rating) %>%
  filter(ratings_count > 0,
         text_reviews_count > 0,
         num_pages > 0,
    average_rating > 0) %>%
  cor() %>%
  corrplot(
type = "lower",
order = "hclust",
method = "color",
addgrid.col = "darkgray",
 outline = T,
 tl.cex = 1,
 tl.col = "black"
)




```

# Clustering top 75 most rated books

```{r fig.width= 5, fig.height=15}

books %>% 
  select(ratings_count,
         text_reviews_count,
         num_pages,
         average_rating, title) %>% 
  arrange(desc(ratings_count)) %>% 
  head(75) %>% 
  remove_rownames() %>% 
  column_to_rownames(var = "title") %>% 
  mutate_all(scale) %>% 
pheatmap(
  border_color = "black",
  cluster_col = T,
  cutree_rows = 3
)
```
