---
title: "TPS May 22"
author: "Ivjyot Singh"
date: "04/05/2022"
output: 
  html_document:
    code_folding: hide
    df_print: paged
    theme: cosmo
    highlight: tango  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, warning = FALSE, message = FALSE)
```


```{r Loading packages}

suppressPackageStartupMessages(library(tidyverse))
library(skimr)
suppressPackageStartupMessages(library(ggstatsplot))
suppressPackageStartupMessages(library(tidymodels))
library(patchwork)
suppressPackageStartupMessages(library(data.table))

```


```{r Reading data}

train <- fread("../input/tabular-playground-series-may-2022/train.csv")
test <- fread("../input/tabular-playground-series-may-2022/test.csv")
sample <- fread("../input/tabular-playground-series-may-2022/sample_submission.csv")

skim(train)
```

<font style="font-family: times, serif; font-size:13pt"> There are 31 predictors ranging from f_00 to f_30. Apart from f_27, which is of character class, all of the predictors are numeric.<br> There is a unique id variable which will not be considered for prediction.<br> We will be using the predictor variables to predict the target variable.<br> Let us first explore these predictor variables.</font>


```{r fig.height=150,fig.width=7} 

f00 <- gghistostats(train,
                    f_00,
                    results.subtitle = FALSE)

f01 <- gghistostats(train,
                    f_01,
                    results.subtitle = FALSE)

f02 <- gghistostats(train,
                    f_02,
                    results.subtitle = FALSE)

f03 <- gghistostats(train,
                    f_03,
                    results.subtitle = FALSE)

f04 <- gghistostats(train,
                    f_04,
                    results.subtitle = FALSE)

f05 <- gghistostats(train,
                    f_05,
                    results.subtitle = FALSE)

f06 <- gghistostats(train,
                    f_06,
                    results.subtitle = FALSE)

f07 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_07)) +
       theme_bw()

f08 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_08)) +
       theme_bw()

f09 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_09)) +
       theme_bw()

f10 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_10)) +
       theme_bw()

f11 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_11)) +
       theme_bw()

f12 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_12)) +
       theme_bw()

f13 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_13)) +
       theme_bw()

f14 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_14)) +
       theme_bw() 

f15 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_15)) +
       theme_bw()

f16 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_16)) +
       theme_bw()

f17 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_17)) +
       theme_bw()

f18 <- ggplot(train) +
       geom_bar(mapping = aes(x=f_18)) +
       theme_bw() 

f19 <- gghistostats(train,
                    f_19,
                    results.subtitle = FALSE)

f20 <- gghistostats(train,
                    f_20,
                    results.subtitle = FALSE)

f21 <- gghistostats(train,
                    f_21,
                    results.subtitle = FALSE)

f22 <- gghistostats(train,
                    f_22,
                    results.subtitle = FALSE)

f23 <- gghistostats(train,
                    f_23,
                    results.subtitle = FALSE)

f24 <- gghistostats(train,
                    f_24,
                    results.subtitle = FALSE)

f25 <- gghistostats(train,
                    f_25,
                    results.subtitle = FALSE)

f26 <- gghistostats(train,
                    f_26,
                    results.subtitle = FALSE)

f28 <- gghistostats(train,
                    f_28,
                    results.subtitle = FALSE)

f29 <- ggpiestats(train,
                  f_29,
                  results.subtitle = FALSE)

f30 <- ggpiestats(train,
                  f_30,
                  results.subtitle = FALSE)

patch1 <- (f00)/ 
          (f01)/ 
          (f02)/ 
          (f03)/
          (f04)/
          (f05)/ 
          (f06)/
          (f07)/
          (f08)/
          (f09)/
          (f10)/
          (f11)/
          (f12)/
          (f13)/
          (f14)/
          (f15)/
          (f16)/
          (f17)/
          (f18)/
          (f19)/ 
          (f20)/
          (f21)/
          (f22)/
          (f23)/ 
          (f24)/
          (f25)/
          (f26)/
          (f28)/
          (f29)/
          (f30)

patch1 + plot_annotation(
         title = "Exploring Numeric Predictors",
         caption = "Data source: Kaggle.com, Tabular Playground Series, May 2022"
                        )
```

<font style="font-family: times, serif; font-size:13pt"> Citation for the visualization above is as follows <br> Patil, I. (2021). Visualizations with statistical details: The 'ggstatsplot' approach.<br> Journal of Open Source Software, 6(61), 3167, doi:10.21105/joss.03167 </font>

        
<font style="font-family: times, serif; font-size:13pt">Work in Progress</font>

