---
title: "Amazon Bestsellers"
output:
  html_document:
    toc: true
    theme: united
---



# Amazon Bestsellers

# Loading libraries

```{r}

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(skimr))
suppressPackageStartupMessages(library(corrplot))
suppressPackageStartupMessages(library(RColorBrewer))
install.packages("factoextra")
library(factoextra)
```

# Loading Data

```{r}

bestsellers <- read.csv("../input/amazon-top-50-bestselling-books-2009-2019/bestsellers with categories.csv")
head(bestsellers, 2)
```

```{r}
str(bestsellers)
```

# Exploring the Data

## Column Names

```{r}

bestsellers %>% colnames()
```

## Checking for missing Values

```{r}

any(is.na(bestsellers))

```

## Data at a glance

```{r}

unique(bestsellers$Year)
unique(bestsellers$Genre)

```

## Data Distribution

```{r}

skim(bestsellers)

```

## all data formats look good, no conversion needed for now

# Data Visualization

# Genres

## Bestsellers distribution by genre

```{r}

bestsellers %>%
  group_by(Genre) %>%
  summarise(books = n()) %>%
  ggplot(aes(x = "", y = books, fill = Genre)) +
  geom_bar(stat = "identity",
           width = 1,
           color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +
  scale_fill_manual(values = c("#ff9900", "#000000"))

```

# Genres through the years

## Bestsellers distribution by genre by year

```{r}

bestsellers %>%
  group_by(Year, Genre) %>%
  summarise(sum = n()) %>%
  ggplot(aes(
    x = Year,
    y = sum,
    fill = Genre
  )) +
  geom_col() +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1)) +
  scale_fill_manual(values = c("#ff9900", "#000000")) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )

  
```

# Correlation Analysis

## Is there any correlation seen between the different numerical variables?

```{r}


bestsellers %>%
  select(User.Rating, Reviews, Price, Year) %>%
  cor() %>%
  corrplot::corrplot(
    type = "lower",
    order = "hclust",
    method = "color",
    addgrid.col = "darkgray",
    outline = T,
    tl.cex = 1,
    tl.col = "black",
    col = brewer.pal(n = 6, name = "RdGy")
  )
```

# User Reviews vs Year

## Most reviewed books

```{r}

bestsellers %>% 
  select(Name, Reviews) %>% 
  arrange(desc(Reviews)) %>% 
  head(20) %>% 
  distinct()
```

## Are the number of reviews changing by year?

### Linear Model

```{r}

bestsellers %>% 
  lm(formula = Year ~ Reviews) %>% 
  summary()
```

### Data Viz

```{r}

bestsellers %>% 
  ggplot(aes(Year, Reviews, color = Genre))+
 geom_jitter()+
 geom_smooth(method = 'lm', formula = y ~ x )+
  theme_minimal() +
    scale_color_manual(values = c("#ff9900", "#000000")) +
    scale_x_continuous(breaks = seq(2009, 2019, by = 1))+
   theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )
```

# Reviews Distribution

```{r}


bestsellers %>% 
  ggplot(aes(Reviews, ..density..)) +
  geom_histogram(fill = "#ff9900", color = 'black',binwidth = 1000) +
    geom_density(alpha = 0.5, fill = "#ff9900") +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank())


```

# User Ratings vs Year

## Highest Rated Books

```{r}

bestsellers %>% 
  select(Name, User.Rating) %>% 
  arrange(desc(User.Rating)) %>% 
  head(20) %>% 
  distinct()
```

## Are users rating the bestsellers differently by year?

### Linear Model

```{r}
bestsellers %>% 
  lm(formula = Year ~ Reviews) %>% 
  summary()
```

### Data Viz

```{r}

bestsellers %>% 
  ggplot(aes(Year, User.Rating, color = Genre))+
 geom_jitter()+
 geom_smooth(method = 'lm', formula = y ~ x )+
  theme_minimal() +
    scale_color_manual(values = c("#ff9900", "#000000")) +
    scale_x_continuous(breaks = seq(2009, 2019, by = 1))+
   theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )
```

# Ratings Distribution

```{r}



bestsellers %>%
  ggplot(aes(User.Rating, ..density..)) +
  geom_histogram(fill = "#ff9900",
                 color = 'black',
                 binwidth = 0.1) +
  geom_density(alpha = 0.5, fill = "#ff9900") +
  theme_minimal() +
  theme(panel.grid.major = element_blank())

```

# Ratings vs Reviews

```{r}


ggplot(bestsellers) +
  aes(
    x = Reviews,
    y = User.Rating,
    colour = Genre,
    size = Reviews
  ) +
  geom_jitter(alpha = 0.45) +
  scale_color_manual(
    values = c(Fiction = "#ff9900",
    `Non Fiction` = "#000000")
  ) +
  theme_minimal()

```

# Price

## Is there a substantial change in price over the years?

### Linear Model

```{r}

bestsellers %>% 
  lm(formula = Year ~ Price) %>% 
  summary()

```

```{r}

bestsellers %>% 
  ggplot(aes(Year, Price, color = Genre))+
 geom_jitter()+
 geom_smooth(method = 'lm', formula = y ~ x )+
  theme_minimal() +
    scale_color_manual(values = c("#ff9900", "#000000")) +
    scale_x_continuous(breaks = seq(2009, 2019, by = 1))+
   theme(
    panel.grid.minor = element_blank(),
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )
```

# Price Distribution

```{r}



bestsellers %>%
  ggplot(aes(Price, ..density..)) +
  geom_histogram(fill = "#ff9900",
                 color = 'black',
                 binwidth = 1.3) +
  geom_density(alpha = 0.5, fill = "#ff9900") +
  theme_minimal() +
  theme(panel.grid.major = element_blank())


```

## Most Expensive Books

```{r}

bestsellers %>% 
  select(Name, Price) %>% 
  arrange(desc(Price)) %>% 
  head(20) %>% 
  distinct() %>% 
    ggplot(aes(x =reorder(Name, Price), y = Price,
              fill = ifelse(Price == max(Price), "red","grey"))) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = c("#000000", "#ff9900")) +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank()
  )
```

# Authors

# Most Instances on the best seller list

```{r}

bestsellers %>% 
  group_by(Author) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(10) %>% 
  ggplot(aes(x =reorder(Author, count), y = count,
              fill = ifelse(count == max(count), "red","grey"))) +
  scale_y_continuous(breaks = seq(0, 13, by = 1))+
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = c("#000000", "#ff9900")) +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank()
  )


```

### What were their books?

```{r}

bestsellers %>% 
  filter(Author=="Jeff Kinney")

```

# Books

## Most instances on the best sellers list

```{r}
bestsellers %>% 
  group_by(Name) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(10) %>% 
  ggplot(aes(x =reorder(Name, count), y = count,
              fill = ifelse(count == max(count), "red","grey"))) +
    scale_y_continuous(breaks = seq(0, 13, by = 1))+
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = c("#000000", "#ff9900")) +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank()
  )
```

# K - Means Clustering

```{r}

data_kmeans <- bestsellers[3:6]
data_kmeans <- data_kmeans %>% 
  slice(1:20)

```

```{r}


library(factoextra)


data_kmeans <- bestsellers[3:6]
data_kmeans <- data_kmeans %>% 
  slice(1:20)

data_kmeans_scaled <- scale(data_kmeans)
data_kmeans <- dist(data_kmeans_scaled)
fviz_nbclust(data_kmeans_scaled, kmeans,
             method = "wss") + # wss means within sum squares
  labs(subtitle = "Elbow Method")

```

```{r}

kmeans_output <- kmeans(data_kmeans_scaled, centers = 3, nstart = 100)
kmeans_output.clusters <- kmeans_output$cluster


```

```{r}
bestsellers_mini <- bestsellers %>% 
  slice(1:20)
```

```{r}

rownames(data_kmeans_scaled) <- paste(bestsellers_mini$Name, 1:dim(bestsellers_mini)[1], sep="_")

```

```{r fig.width= 5, fig.height= 4}

fviz_cluster(list(data = data_kmeans_scaled, cluster = kmeans_output.clusters)) +
  theme_minimal() +
  theme(plot.subtitle = element_text(size = 12,
                               face = "italic"),
  plot.caption = element_text(size = 9),
  plot.title = element_text(size = 15,
                            face = "bold")
) + labs(
  colour = "Cluster",
  fill = "Cluster",
  shape = "Cluster",
)
```

```{r}

test <- table(kmeans_output.clusters, bestsellers_mini$Name)
as.data.frame(test)
```

# Hierarchical clustering

```{r fig.height= 3, fig.width=3}

res <- hcut(data_kmeans_scaled, k = 4, stand = TRUE)
# Visualize
fviz_dend(res, rect = TRUE, cex = 0.3,
          k_colors = c("#00AFBB","#2E9FDF", "#E7B800", "#FC4E07")) +
  theme_minimal()

```
